---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# sisglmlss

## Overview

**`sisglmlss`** is an R package to perform model selection via (iterative) sure independence screening (ISIS)
in generalized linear models for location, scale and shape (GLMLSS). It implements the algorithms `pvanISIS`
and `pvarISIS` proposed in the paper by Amon and Hornik (2022). For details, please see the original paper
and the package documentation.

## Installation

The source code is hosted on [github](https://github.com/jamon-R/sisglmlss). To install the _R_ package, run the following code:

```{r, eval = FALSE, echo = TRUE}
devtools::install_github("jamon-R/sisglmlss")
```

The package requires functionality from the packages `gamlss`, `gamlss.dist` and `gamlss.lasso2`. While the former two are available
on [CRAN](https://cran.r-project.org/), the latter package is only available in a version called `gamlss.lasso`, which does not
perform tuning based on cross-validation in a correct manner. We therefore had to adapt the source code from the corresponding
package ourselves. The corresponding adaptation is also available on [github](https://github.com/jamon-R/gamlss.lasso2) and has to be
installed prior to the installation of `sisglmlss`.

## Usage

The main work horse of the package is the function `sisglmlss`, which allows to perform different variants of
sure independence screening in GLMLSSs. The function offers a lot of flexibility for the user. Specifically,
the user can decide, which family of distributions to use for the response variable, how to tune the shrinkage
parameter in the LASSO step, whether to perform the `pvanISIS` or `pvarISIS` variant, which quantile threshold
to use for the data-driven likelihood thresholding, whether or not to standardize the variables and how many
cores to use for the marginal maximum likelihood computations. Moreover, the user also has full control of the
inner workings of the model fitting, as there are arguments to pass in output from the outer and inner control
functions of the [gamlss](https://cran.r-project.org/web/packages/gamlss/index.html) package. 
